Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-04 submission/NatCom_appendix.tex
made change to table in appendix
full pass to revise cv discussion, revise comments, revise response

%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ImageNet 1K]{
%%        \includegraphics[width=4.9cm]{img/all-imagenet-1k_alpha.png}
%%        \label{fig:imagenet1k-alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 10 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-10_alpha.png}
%%        \label{fig:cifar10.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 100 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-100_alpha.png}
%%        \label{fig:cifar100.alpha}
%%    }
%%    \qquad
%%    \subfigure[ SVHN ]{
%%        \includegraphics[width=4.9cm]{img/all-svhn_alpha.png}
%%        \label{fig:svhn.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CUB 200 ]{
%%        \includegraphics[width=4.9cm]{img/all-cub-200-2011_alpha.png}
%%        \label{fig:cub200.alpha}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different datasets (as segmented in Table~\ref{table:datasets}).
%%            }
%%    \label{fig:DSalphas}
%%\end{figure}
%%
%% 
%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ ResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_01}
%%    }
%%    \subfigure[ SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_02}
%%    }
%%    \subfigure[ DIA-ResNet/DIA-PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_03}
%%    }
%%    \subfigure[ ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_04}
%%    }
%%    \subfigure[ WRN ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_05}
%%    }
%%    \subfigure[ DLA ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_06}
%%    }
%%    \subfigure[ PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_07}
%%    }
%%    \subfigure[ ProxylessNAS ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_08}
%%    }
%%    \subfigure[ VGG/BN-VGG ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_09}
%%    }
%%    \subfigure[ IGCV3 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_10}
%%    }
%%    \subfigure[ EfficientNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_11}
%%    }
%%    \subfigure[ SqueezeNext/SqNxt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_12}
%%    }
%%    \subfigure[ ShuffleNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_13}
%%    }
%%    \subfigure[ DRN-C/DRN-D ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_14}
%%    }
%%    \subfigure[ ESPNetv2 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_15}
%%    }
%%    \subfigure[ HRNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_16}
%%    }
%%    \subfigure[ SqueezeNet/SqueezeResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_17}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different architecture series (as segmented in Table~\ref{table:architectures}).
%%            }
%%    \label{fig:ARCHalphas}
%%\end{figure}
\input{table_RMSE}
\input{table_R2}
\input{table_Ktau}

@@

\michael{The text in this section needs to be changed---probably not removed, but instead discuss things, not point to the figure we remove, and point to the repo. }

\michael{Do we get more visually compelling results if we present figures, but segmented by architectures, as listed in Table~\ref{table:architectures}; if so, perhaps we should put those, so we don't tell R1 that we just removed what looked bad; or maybe actually both, since we segment by dataset in Table~\ref{table:datasets}. }

To explain further how to reproduce our analysis, we run three batches of linear regressions. 
First, at the global level, we divide models by datasets and run regressions separately on all models of a certain dataset, regardless of the architecture. 
At this level, the plots are quite noisy and clustered, as each architecture has its own accuracy trend; but one can
 still see that most plots show positive relationship with positive coefficients. 
% V1 REMOVED FOR V2 % Example regressions are shown in Figure~\ref{fig:DSalphas}, as available in the results notebook.
%%Example regressions are shown in 
%%Figure~\ref{fig:DSalphas}, for models segmented by dataset, as listed in Table~\ref{table:datasets}, 
%%and in 
%%Figure~\ref{fig:ARCHalphas}, for models segmented by architecture, as listed in Table~\ref{table:architectures}.
\michael{Comment here on differences.}

To generate the results in Table~\ref{table:results}, we run linear regressions for each architecture series in Table~\ref{table:architectures}, regressing each empirical Log Norm metric against the reported Top1 (and Top5) errors (as listed on the \texttt{osmr/imgclsmob} github repository README file~\cite{osmr}, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}).
We record the $R^{2}$ and $MSE$ for each metric, averaged over all regressions for all architectures and datasets.
\michael{Mention KTau.}
See Table~\ref{table:RMSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:Ktauresults}.
In the repo, plots are provided for every regression, and more fine grained results may be computed by the reader by analyzing the data in the \texttt{df\_all.xlsx} file.
The final analysis includes 108 regressions in all, those with 4 or more models, with a positive $R^2$.

See
Figure~\ref{fig:summary_regressions_A},
Figure~\ref{fig:summary_regressions_B},
Figure~\ref{fig:summary_regressions_C},
Figure~\ref{fig:summary_regressions_D},
Figure~\ref{fig:summary_regressions_E},
Figure~\ref{fig:summary_regressions_F},
Figure~\ref{fig:summary_regressions_G},
Figure~\ref{fig:summary_regressions_H}, and
Figure~\ref{fig:summary_regressions_A} for more details.
\michael{Put a bit of discussion, e.g., on best and worst.}

\michael{Probably some discussion of why these metrics are the right ones, e.g., as opposed to $p$ values, to address R1 comments.}

>>>>

%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ImageNet 1K]{
%%        \includegraphics[width=4.9cm]{img/all-imagenet-1k_alpha.png}
%%        \label{fig:imagenet1k-alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 10 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-10_alpha.png}
%%        \label{fig:cifar10.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 100 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-100_alpha.png}
%%        \label{fig:cifar100.alpha}
%%    }
%%    \qquad
%%    \subfigure[ SVHN ]{
%%        \includegraphics[width=4.9cm]{img/all-svhn_alpha.png}
%%        \label{fig:svhn.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CUB 200 ]{
%%        \includegraphics[width=4.9cm]{img/all-cub-200-2011_alpha.png}
%%        \label{fig:cub200.alpha}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different datasets (as segmented in Table~\ref{table:datasets}).
%%            }
%%    \label{fig:DSalphas}
%%\end{figure}
%%
%% 
%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ ResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_01}
%%    }
%%    \subfigure[ SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_02}
%%    }
%%    \subfigure[ DIA-ResNet/DIA-PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_03}
%%    }
%%    \subfigure[ ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_04}
%%    }
%%    \subfigure[ WRN ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_05}
%%    }
%%    \subfigure[ DLA ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_06}
%%    }
%%    \subfigure[ PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_07}
%%    }
%%    \subfigure[ ProxylessNAS ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_08}
%%    }
%%    \subfigure[ VGG/BN-VGG ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_09}
%%    }
%%    \subfigure[ IGCV3 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_10}
%%    }
%%    \subfigure[ EfficientNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_11}
%%    }
%%    \subfigure[ SqueezeNext/SqNxt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_12}
%%    }
%%    \subfigure[ ShuffleNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_13}
%%    }
%%    \subfigure[ DRN-C/DRN-D ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_14}
%%    }
%%    \subfigure[ ESPNetv2 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_15}
%%    }
%%    \subfigure[ HRNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_16}
%%    }
%%    \subfigure[ SqueezeNet/SqueezeResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_17}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different architecture series (as segmented in Table~\ref{table:architectures}).
%%            }
%%    \label{fig:ARCHalphas}
%%\end{figure}

\input{table_6}

\input{table_RMSE}
\input{table_R2}
\input{table_Ktau}

@@

\michael{Charles, would you put in a couple of paragraphs about how you generated the tables/figures in the appendix, and a few things we learn from them, i.e., basically enough to convince that reviewer that we paid attention to their concerns.}

\michael{Table~\ref{table:architectures} still needs to be fixed, since it does not include the overall results partitioned by dataset that we had in the old Table~\ref{table:datasets}. }

To explain further how to reproduce our analysis, we run three batches of linear regressions. 
First, at the global level, we divide models by datasets and run regressions separately on all models of a certain dataset, regardless of the architecture. 
At this level, the plots are quite noisy and clustered, as each architecture has its own accuracy trend; but one can
 still see that most plots show positive relationship with positive coefficients. 
% V1 REMOVED FOR V2 % Example regressions are shown in Figure~\ref{fig:DSalphas}, as available in the results notebook.
%%Example regressions are shown in 
%%Figure~\ref{fig:DSalphas}, for models segmented by dataset, as listed in Table~\ref{table:datasets}, 
%%and in 
%%Figure~\ref{fig:ARCHalphas}, for models segmented by architecture, as listed in Table~\ref{table:architectures}.
\michael{Charles, this paragraph is stale since it refers to the old figures that the reviewer did not like, so would you update it.}

To generate the results in Table~\ref{table:results}, we run linear regressions for each architecture series in Table~\ref{table:architectures}, regressing each empirical Log Norm metric against the reported Top1 (and Top5) errors (as listed on the \texttt{osmr/imgclsmob} github repository README file~\cite{osmr}, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}).
We record the $RMSE$, $R^{2}$, and Kendall-$\tau$ for each metric, averaged over all regressions for all architectures and datasets;
see Table~\ref{table:RMSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:Ktauresults}, respectively.
\michael{Charles, the label is broken in the caption of Table~\ref{table:RMSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:Ktauresults}.}
In the repo, plots are provided for every regression, and more fine grained results may be computed by the reader by analyzing the data in the \texttt{df\_all.xlsx} file.
The final analysis includes 108 regressions in all, those with 4 or more models, with a positive $R^2$.

See
Figure~\ref{fig:summary_regressions_A},
Figure~\ref{fig:summary_regressions_B},
Figure~\ref{fig:summary_regressions_C},
Figure~\ref{fig:summary_regressions_D},
Figure~\ref{fig:summary_regressions_E},
Figure~\ref{fig:summary_regressions_F},
Figure~\ref{fig:summary_regressions_G},
Figure~\ref{fig:summary_regressions_H}, and
Figure~\ref{fig:summary_regressions_I} for more details.
\michael{Charles, would you put a bit of discussion, e.g., on best and worst, again just a teaser to satisfy that reviewer.}

### 2021-01-04 submission/NatCom_cv_models.tex
full pass to revise cv discussion, revise comments, revise response

We examine the performance of the four quality metrics (Log Frobenius norm, Log Spectral norm, Weighted Alpha, and Log $\alpha$-Norm) applied to each of the VGG, ResNet, ResNet-1K, and DenseNet series.
Figure~\ref{fig:vgg-metrics} 
plots the four quality metrics versus reported test accuracies~\cite{pytorch},% 
\footnote{These test accuracies have been previously reported and made publicly-available by others.  We take them as given.  We do not attempt to reproduce/verify them, since we do not permit ourselves access to training/test data.}
as well as a basic linear regression line, for the VGG series.
All four metrics correlate quite well with reported Top1 accuracies, with smaller norms and smaller values of $\hat{\alpha}$ implying better generalization (i.e., greater accuracy, lower error). 
\michael{The following, text and numbers, will need to be updated once we finalize the figures/tables.}
The Log $\alpha$-Norm metric ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$) performs best (RMSE of $0.42$, $R^2$ of $XXX$, and Kendall-$\tau$ of $XXX$, see Table~\ref{table:cv-models}); and the Weighted Alpha metric ($\hat\alpha =\alpha\log\lambda_{max} $) performs second best (RMSE of $0.48$, $R^2$ of $XXX$, and Kendall-$\tau$ of $XXX$, see Table~\ref{table:cv-models}).
\michael{Put comment on why these three metrics, that HT-SR says that $\hat{\alpha}$ should exhibit good linear correlation, and a few comments on non-normality to address R1 concerns.}
\charles{The Log Spectral Norm metric correlates very well with small, simpler data sets like the VGG and DenseNet architectures, however, when moving to the larger and more complex ResNet series, the PL-based metrics Log $\alpha$-Norm ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$) 
and  Weighted Alpha ($\hat\alpha =\alpha\log\lambda_{max} $) metrics perform better across all measures.}

@@

    \subfigure[ ResNet, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet_log_alpha_norm_accs.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet-1K_log_alpha_norm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    \caption{Comparison of Average $\alpha$-Norm quality metric versus reported Top1 test accuracy for the ResNet and ResNet-1K pretrained (pyTorch) models. 
             \michael{FROM V1: Symbols and text are way to small on these and other figures; axes/ticks way too small; need different symbols, not just red versus green; etc.}
\charles{See changes}
            }
    \label{fig:cv2-accuracy}
\end{figure}

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|c|}
\hline
 Series                      & \#                    & Metric         & $\langle\log\Vert\mathbf{W}\Vert^{2}_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
\multirow{3}{4em}{VGG}       & \multirow{3}{1em}{6}  & RMSE           & 0.56 & \textbf{0.23} & 0.48          & 0.34  \\
                             &                       & $R^2$          & 0.88 & \textbf{0.98} &  0.92         &  0.96           \\
                             &                       & Kendall-$\tau$ & -0.79 &  \textbf{-0.93} & \textbf{-0.93} & \textbf{-0.93}        \\
\hline
\multirow{3}{4em}{ResNet}    & \multirow{3}{1em}{5}  & RMSE           &  0.9 & 0.97 & \textbf{0.61} & 0.66        \\
                             &                       & $R^2$          &  0.92 &  0.9 &  \textbf{0.96}   &  0.9         \\
                             &                       & Kendall-$\tau$ &  -1.0 &  -1.0 &  -1.0          &  -1.0        \\
\hline
\multirow{3}{4em}{ResNet-1K} & \multirow{3}{1em}{19} & RMSE           &  2.4 & 2.8  & \textbf{1.8}  & 1.9          \\
                             &                       & $R^2$          &  0.81 &  0.74 &  \textbf{0.89}    &  0.88           \\
                             &                       & Kendall-$\tau$ &  -0.79 &  -0.79 &  \textbf{-0.89}  &  -0.88           \\
\hline
\multirow{3}{4em}{DenseNet}  & \multirow{3}{1em}{4}  & RMSE           &  0.3 & \textbf{0.11}  & 0.16 & 0.21       \\
                             &                       & $R^2$          &  0.93 &  \textbf{0.99} &  0.98      &  0.97    \\
                             &                       & Kendall-$\tau$ &  -1.0 &  -1.0 &  -1.0         &  -1.0     \\
\hline
\end{tabular}
\end{center}
\caption{Quality metrics 
         (RMSE, smaller is better; $R^2$, XXX is better; and Kendall-$\tau$ rank correlation, XXX is better)
         for reported Top1 test error for pretrained models in each architecture series.  
         Column \# refers to number of models.  
         VGG, ResNet, and DenseNet were pretrained on ImageNet.  
         ResNet-1K was pretrained on ImageNet-1K. 
}
\label{table:cv-models}
\end{table}

\michael{The following, text and numbers, will need to be updated once we finalize the figures/tables.}
Overall, all metrics perform relatively well; the Weighted Alpha metric performs best; and the Log $\alpha$-Norm metric performs second best.
See Table~\ref{table:cv-models} for a summary of results for Top1 accuracies for all four metrics for the VGG, ResNet, ResNet-1K, and DenseNet series.
Similar results are obtained for the Top5 accuracies.
These model series are all very well-trodden, and our results indicate that norm-based metrics and PL-based metrics can both distinguish among a series of well-trained versus very-well-trained models, with PL-based metrics performing somewhat (i.e., quantitatively) better.
The DenseNet series has similar behavior.
(These and many other such plots can be seen on our publicly-available~repo.)

To examine how the four quality metrics depend on data set size, we look at results on ResNet versus ResNet-1K.
Figure~\ref{fig:cv2-accuracy} compares the Log $\alpha$-Norm metric for the full ResNet model, trained on the full ImageNet dataset, against the ResNet-1K model, trained on a much smaller ImageNet-1K data set.
\michael{The following, text and numbers, will need to be updated once we finalize the figures/tables.}
The Log $\alpha$-Norm is much better than the Log Frobenius/Spectral norm metrics (although, as Table~\ref{table:cv-models} shows, it is slightly worse than the Weighted Alpha metric).
The ResNet series has strong correlation (RMSE of $0.66$, $R^2$ of $XXX$, and Kendall-$\tau$ of $XXX$), whereas the ResNet-1K series also shows good but weaker correlation (much larger RMSE of $1.9$, $R^2$ of $XXX$, and Kendall-$\tau$ of $XXX$).
(Other metrics exhibit similar behavior.)
The higher quality data set shows a better fit, even with fewer data~points.

>>>>

We examine the performance of the four quality metrics (Log Frobenius norm, Log Spectral norm, Weighted Alpha, and Log $\alpha$-Norm) applied to each of the VGG, ResNet, ResNet-1K, and DenseNet series.
%
Figure~\ref{fig:vgg-metrics} plots the four quality metrics versus reported test accuracies~\cite{pytorch},% 
\footnote{These test accuracies have been previously reported and made publicly-available by others.  We take them as given.  We do not attempt to reproduce/verify them, since we do not permit ourselves access to training/test data.}
as well as a basic linear regression line, for the VGG series.
Here, smaller norms and smaller values of $\hat{\alpha}$ imply better generalization (i.e., greater accuracy, lower error). 
Quantitatively, Log Spectral norm is the best; but, visually, all four metrics correlate quite well with reported Top1 accuracies.
The DenseNet series has similar behavior.
(These and many other such plots can be seen on our publicly-available~repo.)

To examine visually how the four quality metrics depend on data set size on a larger, more complex model series, we next look at results on ResNet versus ResNet-1K.
Figure~\ref{fig:cv2-accuracy} compares the Log $\alpha$-Norm metric for the full ResNet model, trained on the full ImageNet dataset, against the ResNet-1K model, trained on a much smaller ImageNet-1K data set.
Here, the Log $\alpha$-Norm is much better than the Log Frobenius/Spectral norm metrics (although, as Table~\ref{table:cv-models} shows, it is slightly worse than the Weighted Alpha metric).
The ResNet series has strong correlation (RMSE of $0.66$, $R^2$ of $0.9$, and Kendall-$\tau$ of $-1.0$), whereas the ResNet-1K series also shows good but weaker correlation (much larger RMSE of $1.9$, $R^2$ of $0.88$, and Kendall-$\tau$ of $-0.88$).
%%(Other metrics exhibit similar behavior.)
%%The higher quality data set shows a better fit, even with fewer data~points.

@@

    \subfigure[ ResNet, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet_log_alpha_norm_accs.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet-1K_log_alpha_norm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    \caption{Comparison of Average $\alpha$-Norm quality metric versus reported Top1 test accuracy for the ResNet and ResNet-1K pretrained (pyTorch) models. 
             Metrics fit by linear regression, RMSE, R2, and the Kendal-tau rank correlation metric reported.  
            }
    \label{fig:cv2-accuracy}
\end{figure}

See Table~\ref{table:cv-models} for a summary of results for Top1 accuracies for all four metrics for the VGG, ResNet, ResNet-1K, and DenseNet series.
Similar results are obtained for the Top5 accuracies.
The Log Frobenius norm performs well but not extremely well;
the Log Spectral norm performs very well on smaller, simpler models like the VGG and DenseNet architectures; and, 
when moving to the larger, more complex ResNet series, the PL-based metrics, Weighted Alpha and the Log $\alpha$-Norm, perform the best.
Overall, though, these model series are all very well-trodden; and our results indicate that norm-based metrics and PL-based metrics can both distinguish among a series of well-trained versus very-well-trained models, with PL-based metrics performing somewhat (i.e., quantitatively) better on the larger, more complex ResNet series.

%%\michael{Put comment on why these three metrics, that HT-SR says that $\hat{\alpha}$ should exhibit good linear correlation, and a few comments on non-normality to address R1 concerns.}

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|c|}
\hline
 Series                      & \#                    & Metric         & $\langle\log\Vert\mathbf{W}\Vert^{2}_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
\multirow{3}{4em}{VGG}       & \multirow{3}{1em}{6}  & RMSE           & 0.56 & \textbf{0.23} & 0.48          & 0.34  \\
                             &                       & $R^2$          & 0.88 & \textbf{0.98} &  0.92         &  0.96           \\
                             &                       & Kendall-$\tau$ & -0.79 &  \textbf{-0.93} & \textbf{-0.93} & \textbf{-0.93}        \\
\hline
\multirow{3}{4em}{ResNet}    & \multirow{3}{1em}{5}  & RMSE           &  0.9 & 0.97 & \textbf{0.61} & 0.66        \\
                             &                       & $R^2$          &  0.92 &  0.9 &  \textbf{0.96}   &  0.9         \\
                             &                       & Kendall-$\tau$ &  -1.0 &  -1.0 &  -1.0          &  -1.0        \\
\hline
\multirow{3}{4em}{ResNet-1K} & \multirow{3}{1em}{19} & RMSE           &  2.4 & 2.8  & \textbf{1.8}  & 1.9          \\
                             &                       & $R^2$          &  0.81 &  0.74 &  \textbf{0.89}    &  0.88           \\
                             &                       & Kendall-$\tau$ &  -0.79 &  -0.79 &  \textbf{-0.89}  &  -0.88           \\
\hline
\multirow{3}{4em}{DenseNet}  & \multirow{3}{1em}{4}  & RMSE           &  0.3 & \textbf{0.11}  & 0.16 & 0.21       \\
                             &                       & $R^2$          &  0.93 &  \textbf{0.99} &  0.98      &  0.97    \\
                             &                       & Kendall-$\tau$ &  -1.0 &  -1.0 &  -1.0         &  -1.0     \\
\hline
\end{tabular}
\end{center}
\caption{Quality metrics 
         (for RMSE, smaller is better; for $R^2$, larger is better; and for Kendall-$\tau$ rank correlation, larger magnitude is better)
         for reported Top1 test error for pretrained models in each architecture series.  
         Column \# refers to number of models.  
         VGG, ResNet, and DenseNet were pretrained on ImageNet.  
         ResNet-1K was pretrained on ImageNet-1K. 
}
\label{table:cv-models}
\end{table}

\michael{Charles, any more sentences to add to the last three paragraphs to clarify anything?  If not, then just comment out this comment.}

### 2021-01-04 submission/NatCom_overall_approach.tex
full pass to revise cv discussion, revise comments, revise response

Consider the objective/optimization function (parameterized by $\mathbf{W}_{l}$s and $\mathbf{b}_{l}$s) for a DNN with $L$ layers, and weight matrices $\mathbf{W}_{l}$ and bias vectors $\mathbf{b}_{l}$, as 
the minimization of a general loss function $\mathcal{L}$ over the training data instances and labels, $\{\mathbf{x}_{i},y_{i}\}\in\mathcal{D}$.
For a typical supervised classification problem, the goal of training is to construct (or learn) $\mathbf{W}_{l}$ and $\mathbf{b}_{l}$ that capture correlations in the data, in the sense of solving
\begin{equation}
\underset{\mathbf{W}_{l},\mathbf{b}_{L}}{\text{argmin}}\;\sum_{i=1}^{N}\left(\mathcal{L}(E_{DNN}(\mathbf{x}_{i})-y_{i})\right)  ,
\end{equation}
\michael{how precisely to change eqn for R3 comment}
where the loss function $\mathcal{L}(\cdot)$ can take on a myriad of forms~\cite{JC17_TR}, and where the energy (or optimization) landscape function
\begin{equation}
%E_{DNN}=h_{L}(\mathbf{W}_{L}\times h_{L-1}(\mathbf{W}_{L-1}\times h_{L-2}(\cdots)+\mathbf{b}_{L-1})+\mathbf{b}_{L})
E_{DNN} = f(\mathbf{x}_{i} ; \mathbf{W}_{1},\ldots,\mathbf{W}_{L},\mathbf{b}_{1},\ldots,\mathbf{b}_{L})
\label{eqn:dnn_energy}
\end{equation}
\michael{sentences around here probably need to be changed in light of change to that eqn R3 wanted}
depends parametrically on the weights and biases.
\michael{FROM V1: See comments for math equations.}
For a trained model, $E_{DNN}$ does not explicitly depend on the data, but rather it maps data instance vectors ($\mathbf{x}_i$ values) to predictions ($y_{i}$ labels).
\michael{FROM V1: Mark found that sentence confusing.}
Therefore, one can analyze $E_{DNN}$ in the absence of any training or test~data.

>>>>

Consider the objective/optimization function (parameterized by $\mathbf{W}_{l}$s and $\mathbf{b}_{l}$s) for a DNN with $L$ layers, and weight matrices $\mathbf{W}_{l}$ and bias vectors $\mathbf{b}_{l}$, as 
the minimization of a general loss function $\mathcal{L}$ over the training data instances and labels, $\{\mathbf{x}_{i},y_{i}\}\in\mathcal{D}$.
For a typical supervised classification problem, the goal of training is to construct (or learn) $\mathbf{W}_{l}$ and $\mathbf{b}_{l}$ that capture correlations in the data, in the sense of solving
\begin{equation}
%%%\underset{\mathbf{W}_{l},\mathbf{b}_{L}}{\text{argmin}}\;\sum_{i=1}^{N}\left(\mathcal{L}(E_{DNN}(\mathbf{x}_{i})-y_{i})\right)  ,
\underset{\mathbf{W}_{l},\mathbf{b}_{L}}{\text{argmin}}\;\sum_{i=1}^{N} \mathcal{L}(E_{DNN}(\mathbf{x}_{i}),y_{i})   ,
\end{equation}
where the loss function $\mathcal{L}(\cdot,\cdot)$ can take on a myriad of forms~\cite{JC17_TR}, and where the energy (or optimization) landscape function
\begin{equation}
%E_{DNN}=h_{L}(\mathbf{W}_{L}\times h_{L-1}(\mathbf{W}_{L-1}\times h_{L-2}(\cdots)+\mathbf{b}_{L-1})+\mathbf{b}_{L})
E_{DNN} = f(\mathbf{x}_{i} ; \mathbf{W}_{1},\ldots,\mathbf{W}_{L},\mathbf{b}_{1},\ldots,\mathbf{b}_{L})
\label{eqn:dnn_energy}
\end{equation}
depends parametrically on the weights and biases.
For a trained model, the form of the function $E_{DNN}$ does not explicitly depend on the data (but it does explicitly depend on the weights and biases).
The function $E_{DNN}$ maps data instance vectors ($\mathbf{x}_i$ values) to predictions ($y_{i}$ labels), and thus the output of this function does depend on the data.
Therefore, one can analyze the form of $E_{DNN}$ in the absence of any training or test~data.
